Object Capability Patterns:\\Policies and Specifications

### 2017-08-18 article.tex
update

However, \textsc{gpe} only postulates the existence of some object with some capability iff there exists some object with some path, and says nothing about how the objects are connected. From the connectivity begets connectivity rule, \textsc{pec}, and \textsc{gpe}, we construct global path-execution relationships over the entire system:
\begin{logic}
\hrule\null
\textsc{\normalsize *Global Path-Execution Connect. (GPEC)}\\
M,\losigma\ \loturns\ MayAccess$^{Ind,Now}$(o,o')\linebreak
\ablock \loiff\linebreak
\ablock \loexists X*\loin{Obj}. $[$MayAccess$^{Ind,Now}$(o, X*) \loand\linebreak
\ablock \ablock \ablock \quad MayAccess$^{Dir,Now}$(X*,o')$]$
\linebreak\\
\textit{By contraposition,} \\
M,\losigma\ \loforall X*\loin{Obj}. $[$\loneg MayAccess$^{Ind,Now}$(o, X*) \loor\linebreak
\ablock \ablock \ablock \quad \loneg MayAccess$^{Dir,Now}$(X*,o')$]$\linebreak
\ablock \loiff\linebreak
\ablock \loneg MayAccess$^{Ind,Now}$(o,o')\linebreak
\hrule
\end{logic}
\textsc{gpec} introduces an intermediate object X* between o and o' that makes explicit the missing connection in \textsc{gpe}.\\

@@

The power in \textsc{gpec} lies in the recursive predicate MayAccess$^{Ind,Now}$(o, X*) that can eventually be expanded into a set of MayAccess$^{Dir,Now}$ predicates that finishes with terminating predicate MayAccess$^{Ind,Now}$(o, o), where the terminating predicate will always be true, unless the object o does not exist in \losigma.
We now look for a relation between a path configuration at a state \losigma\ ($Now$) and eventual path configurations in states \losigma' arising from \losigma\ ($Eve$).\vfill
\begin{minipage}[b]{\linewidth}
\begin{logic}
\hrule\null
\textsc{\normalsize *Eventual Path Connectivity 1 (EPC1)}\\
M,\losigma\ \loturns\ MayAccess$^{Ind,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj. $\{[$MayAccess$^{Ind,Now}$(o,X*)\linebreak
\ablock \ablock \ablock \ablock\loor \linebreak
\ablock \ablock \ablock \quad\: MayAccess$^{Dir,Now}$(X*,o)$]$\linebreak
\ablock \ablock \ablock \quad \loand \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(X*,o')$\}$
\linebreak \\
\textit{By contraposition,}\linebreak
M,\losigma\ \loturns\ \linebreak
\ablock \loforall X*\loin Obj. $\{[$\loneg MayAccess$^{Ind,Now}$(o,X*)\linebreak
\ablock \ablock \ablock \ablock \quad \loand \linebreak
\ablock \ablock \ablock \quad\: \loneg MayAccess$^{Dir,Now}$(X*,o)$]$\linebreak
\ablock \ablock \ablock \quad \loor \linebreak
\ablock \ablock \ablock \quad \loneg MayAccess$^{Ind,Eve}$(X*,o')$\}$\linebreak
\ablock \loimplies\linebreak
	\ablock\loneg MayAccess$^{Ind,Eve}(o,o')$\linebreak
\hrule
\end{logic}
\end{minipage}
\textsc{epc1} has the meaning that if an object o has an eventual path to o' in some arising state \losigma', then there must exist an object X* that has an eventual path to o', and there must exist a way for o to have a path to X* in \losigma'. o either must already have a path to X* in \losigma, or that it will eventually receive the capability of X* in \losigma'. \textsc{epc1} is actually a formal representation of connectivity begets connectivity across time:

@@

\begin{logic}
\hrule\null
\textsc{\normalsize *Eventual Path Connectivity 2 (EPC2)}\\
M,\losigma\ \loturns\ MayAccess$^{Ind,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj.$\{$\linebreak
\ablock \ablock $[$\null
\textcolor{red}{\loexists X$^1$\loin{Obj}. MayAccess$^{Ind,Now}$(o, X$^1$) \loand\linebreak
\ablock \ablock \ablock \ablock \quad MayAccess$^{Dir,Now}$(X$^1$,X*)\linebreak
}
\ablock \ablock \quad \loor \linebreak
\ablock \ablock MayAccess$^{Dir,Now}$(X*,o)$ ]$\linebreak
\ablock \ablock \loand \linebreak
\textcolor{blue}{
\ablock \ablock \loexists Y*\loin Obj.$\{[$MayAccess$^{Ind,Now}$(X*,Y*)\linebreak
\ablock \ablock \ablock \ablock \quad \quad \loor \linebreak
\ablock \ablock \ablock \ablock \quad MayAccess$^{Dir,Now}$(Y*,X*)$]$\linebreak
\ablock \ablock \ablock \ablock \quad \loand \linebreak
\ablock \ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(Y*,o')$\}$
}\linebreak
\ablock \ablock $\}$
\linebreak \\
\textit{By contraposition,}\linebreak
M,\losigma\ \loturns\ \linebreak
\ablock \loforall X*\loin Obj.$\{$\linebreak
\ablock \quad $[$\null
\textcolor{red}{\loforall X$^1$\loin{Obj}. \loneg MayAccess$^{Ind,Now}$(o,X$^1$) \loor\linebreak
\ablock \ablock \ablock \ablock \loneg MayAccess$^{Dir,Now}$(X$^1$,X*)\linebreak
}
\ablock \ablock \quad \loand \linebreak
\ablock \quad \loneg MayAccess$^{Dir,Now}$(X*,o)$ ]$\linebreak
\ablock \ablock \loor \linebreak
\textcolor{blue}{
\ablock \loforall Y*\loin Obj. $\{[$\loneg MayAccess$^{Ind,Now}$(X*,Y*)\linebreak
\ablock \ablock \ablock \ablock \quad \loand \linebreak
\ablock \ablock \ablock \quad\: \loneg MayAccess$^{Dir,Now}$(Y*,X*)$]$\linebreak
\ablock \ablock \ablock \quad \loor \linebreak
\ablock \ablock \ablock \quad \loneg MayAccess$^{Ind,Eve}$(Y*,o')$\}$
}\linebreak
\ablock \loimplies\linebreak
	\ablock\loneg MayAccess$^{Ind,Eve}(o,o')$\linebreak
\hrule
\end{logic}

@@

\begin{logic}
\hrule\null
\textsc{\normalsize *Eventual Path Connectivity 3*** (EPC3***)}\\
M,\losigma\ \loturns\ MayAccess$^{Ind,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*, x$^{1...n}$\loin Obj.$\{[$MayAccess$^{Ind,Now}$(o,o)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(o,x$^1$)\linebreak
\ablock \ablock \ablock \ablock \ablock $\vdots$\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^{n-1}$,x$^n$)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^n$,X*)$]$\linebreak
\ablock \ablock \ablock \ablock \quad\: \loor \linebreak
\ablock \ablock \ablock \ablock \quad\: MayAccess$^{Dir,Now}$(X*,o)$\}$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(X*,o')\linebreak\\
\ablock \textit{where if o exists in \losigma,} \linebreak
\ablock \loturns\ MayAccess$^{Ind,Now}$(o,o) is true\linebreak\linebreak\
\ablock \textit{where if o' exists in some \losigma',}\linebreak
\ablock \loturns\ MayAccess$^{Ind,Eve}$(o',o') is true\linebreak
\hrule
\hrule
\end{logic}

@@

\begin{logic}
\hrule\null
\textsc{\normalsize *Eventual Execution Connectivity (EEC)}\\
M,\losigma\ \loturns\ MayAccess$^{Dir,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj.$[($MayAccess$^{Dir,Now}$(o,X*) \loor \linebreak
\ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(X*,o)$)$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \ablock \ablock MayAccess$^{Dir,Eve}$(X*,o')$]$
\linebreak \\
\textit{By contraposition,}\linebreak
M,\losigma\ \loturns\ 
\loforall X*\loin Obj. $\{[$\loneg MayAccess$^{Dir,Now}$(o,X*) \loand \linebreak
\ablock \ablock \ablock \ablock \quad \loneg MayAccess$^{Dir,Now}$(X*,o)$]$\linebreak
\ablock \ablock \ablock \ablock \loor \linebreak
\ablock \ablock \ablock \ablock \loneg $[$MayAccess$^{Dir,Eve}$(X*,o')$]\}$\linebreak
\ablock \loimplies\linebreak
	\ablock\loneg MayAccess$^{Dir,Eve}(o,o')$\linebreak
\hrule
\end{logic}
The power of \textsc{eec} is similar to \textsc{epc1}\ in that it allows an arbitrary recursive expansion of the MayAccess$^{Dir,Eve}$(X*,o') till the terminating MayAccess$^{Dir,Eve}$(o',o').\\

@@

\begin{logic}
\hrule\null
\textsc{\normalsize *Necessary Path Condition 2 (NPC2)}\\
M,\losigma\ \loturns\ MayAffect$^{Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj.$[($MayAccess$^{Ind,Now}$(o,X*) \loor \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Dir,Now}$(X*,o)$)$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(X*,o')$]$
\linebreak \\
\textit{By contraposition,}\linebreak
M,\losigma\ \loturns\ 
\loforall X*\loin Obj. $[$\loneg MayAccess$^{Ind,Now}$(o,X*) \loand \linebreak
\ablock \ablock \ablock \ablock \loneg MayAccess$^{Dir,Now}$(X*,o)$]$\linebreak
\ablock \ablock \ablock \ablock \loor \linebreak
\ablock \ablock \ablock \ablock \loneg MayAccess$^{Ind,Eve}$(X*,o')$]$\linebreak
\ablock \loimplies \linebreak
	\ablock\loneg MayAffect$^{Eve}(o,o')$\linebreak
\hrule
\end{logic}
, where \textsc{npc2} is similar to \textsc{epc2}, where we can always use \textsc{gpec} to expand indirect paths into direct capabilities till we reach the terminating origin o and recursively use \textsc{epc2} to expand MayAccess$^{Ind,Eve}$(X*,o') till we reach the terminating MayAccess$^{Ind,Eve}$(o',o'). The final result through such as expansion is similar to \textsc{epc3***}. We use \textsc{epc3***} to make explicit the relationship between a configuration of direct capabilities between objects at \losigma, and the ability to modify state at some arising \losigma', which we call \textsc{ncc3***}:
\begin{logic}
\hrule\null
\textsc{\normalsize *Necessary Capability Condition 3*** (NCC3***)}\\
M,\losigma\ \loturns\ MayAffect$^{Ind,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*, x$^{1...n}$\loin Obj.$\{[$MayAccess$^{Ind,Now}$(o,o)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(o,x$^1$)\linebreak
\ablock \ablock \ablock \ablock \ablock $\vdots$\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^{n-1}$,x$^n$)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^n$,X*)$]$\linebreak
\ablock \ablock \ablock \ablock \quad\: \loor \linebreak
\ablock \ablock \ablock \ablock \quad\: MayAccess$^{Dir,Now}$(X*,o)$\}$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(X*,o')\linebreak\\

\ablock \textit{where if o exists in \losigma,} \linebreak
\ablock \loturns\ MayAccess$^{Ind,Now}$(o,o) is true\linebreak\linebreak\
\ablock \textit{where if o' exists in some \losigma',}\linebreak
\ablock \loturns\ MayAccess$^{Ind,Eve}$(o',o') is true\linebreak
\hrule
\end{logic}

@@

We can also show dominance by extending our necessary capability condition \textsc{ncc3***}. If we can guarantee that Y* is the only object in the system that holds the direct capability of o', and we deny Y* a direct path to o', then we know the last object in the eventual path to o' is Y* and we can simply expand the last term in \textsc{ncc3***} to state explicitly that Y* has to be the object that connects directly eventually to o':
\begin{minipage}{\linewidth}
\begin{logic}
\hrule\null
\textsc{\normalsize *Necessary Dominating Condition*** (NDC***)}\\
If Y* dominates o' then:\\
M,\losigma\ \loturns\ MayAffect$^{Ind,Eve}$(o,o') \loand\ Dom(Y*,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*, x$^{1...n}$\loin Obj.$\{[$MayAccess$^{Ind,Now}$(o,o)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(o,x$^1$)\linebreak
\ablock \ablock \ablock \ablock \ablock $\vdots$\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^{n-1}$,x$^n$)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^n$,X*)$]$\linebreak
\ablock \ablock \ablock \ablock \quad\: \loor \linebreak
\ablock \ablock \ablock \ablock \quad\: MayAccess$^{Dir,Now}$(X*,o)$\}$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \loexists Y*\loin{AttenObj}.$[$MayAccess$^{Ind,Eve}$(X*, Y*) \loand\linebreak
\ablock \ablock \ablock \ablock \ablock \quad MayAccess$^{Dir,Eve}$(Y*,o')$]$

\ablock \textit{where if o exists in \losigma,} \linebreak
\ablock \loturns\ MayAccess$^{Ind,Now}$(o,o) is true\linebreak\linebreak\
\ablock \textit{where if o' exists in some \losigma',}\linebreak
\ablock \loturns\ MayAccess$^{Dir,Eve}$(o',o') is true\linebreak
\hrule
\end{logic}
\end{minipage}\linebreak\\
Our analysis shows the importance of attenuating objects---objects that perform their roles as \textit{defensive} objects along the eventual paths to our protected objects. If the protected object can guarantee through the system of configuration that those attenuating objects are the \textit{only} objects in the entire system that holds its capability in \textit{all} eventual states, then the protected object can dictate the conditions and degree of control on how it can be used by untrusted objects in all eventual states through those attenuating objects. This ability of the protected object to dictate control across time and conditions enables cooperation, where conditions on how the protected object will cooperate is written in those attenuating objects.\\

@@

\begin{minipage}{\linewidth}
\begin{logic}
\hrule\null
\textsc{\normalsize *Necessary Node Condition***}\\
If Y* dominates o' then:\\
M,\losigma\ \loturns\ \loforall o\loin Obj, rn\loin ReNode, n\loin Node\linebreak
ReNode\loin Obj, Node\loin Obj.\linebreak
\ablock MayAffect$^{Eve}$(o,n) \loand\ Dom(RN*,n)\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj.$\{[$MayAccess$^{Ind,Eve}$(o,X*)\linebreak
\ablock \ablock \ablock \ablock \quad\: \loor \linebreak
\ablock \ablock \ablock \ablock \quad\: MayAccess$^{Dir,Now}$(X*,o)$\}$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \loexists rn\loin{RN*}.$[$MayAccess$^{Ind,Eve}$(X*, rn) \loand\linebreak
\ablock \ablock \ablock \ablock \ablock \quad MayAccess$^{Dir,Eve}$(rn,o')$]$

\ablock \textit{where if o exists in \losigma,} \linebreak
\ablock \loturns\ MayAccess$^{Ind,Now}$(o,o) is true\linebreak\linebreak\
\ablock \textit{where if o' exists in some \losigma',}\linebreak
\ablock \loturns\ MayAccess$^{Dir,Eve}$(o',o') is true\linebreak
\hrule

>>>>

However, \textsc{gpe} only postulates the existence of some object with some capability iff there exists some object with some path, and says nothing about how the objects are connected. From the connectivity begets connectivity rule, \textsc{pec}, and \textsc{gpe}, we construct global path-execution relationships over the entire system:
\begin{logic}
\hrule\null
\textsc{\normalsize *Global Path-Execution Connect. (GPEC)}\\
M,\losigma\ \loturns\ MayAccess$^{Ind,Now}$(o,o')\linebreak
\ablock \loiff\linebreak
\ablock \loexists X*\loin{Obj}. $[$MayAccess$^{Ind,Now}$(o, X*) \loand\linebreak
\ablock \ablock \ablock \quad MayAccess$^{Dir,Now}$(X*,o')$]$
\\
\ablock \textit{where if z exists in \losigma,} \linebreak
\ablock \loturns\ MayAccess$^{Ind,Now}$(z,z) is true \linebreak
\\
\textit{By contraposition,} \\
M,\losigma\ \loforall X*\loin{Obj}. $[$\loneg MayAccess$^{Ind,Now}$(o, X*) \loor\linebreak
\ablock \ablock \ablock \quad \loneg MayAccess$^{Dir,Now}$(X*,o')$]$\linebreak
\ablock \loiff\linebreak
\ablock \loneg MayAccess$^{Ind,Now}$(o,o')

\hrule
\end{logic}
\textsc{gpec} introduces an intermediate object X* between o and o' that makes explicit the missing connection in \textsc{gpe}.\\

@@

The power in \textsc{gpec} lies in the recursive predicate MayAccess$^{Ind,Now}$(o, X*) that can eventually be expanded into a set of MayAccess$^{Dir,Now}$ predicates that finishes with terminating predicate MayAccess$^{Ind,Now}$(o, o), where the terminating predicate will always be true, unless the object o does not exist in \losigma.
We now look for a relation between a path configuration at a state \losigma\ ($Now$) and eventual path configurations in states \losigma' arising from \losigma\ ($Eve$).\vfill
\begin{minipage}{\linewidth}
\begin{logic}
\hrule\null
\textsc{\normalsize *Eventual Path Connectivity 1 (EPC1)}\\
M,\losigma\ \loturns\ MayAccess$^{Ind,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj. $\{[$MayAccess$^{Ind,Now}$(o,X*)\linebreak
\ablock \ablock \ablock \ablock\loor \linebreak
\ablock \ablock \ablock \quad\: MayAccess$^{Dir,Now}$(X*,o)$]$\linebreak
\ablock \ablock \ablock \quad \loand \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(X*,o')$\}$
\\
\ablock \textit{where if z' exists in \losigma,} \linebreak
\ablock \loturns\ MayAccess$^{Ind,Eve}$(z',z') is true \linebreak
\\
\textit{By contraposition,}\linebreak
M,\losigma\ \loturns\ \linebreak
\ablock \loforall X*\loin Obj. $\{[$\loneg MayAccess$^{Ind,Now}$(o,X*)\linebreak
\ablock \ablock \ablock \ablock \quad \loand \linebreak
\ablock \ablock \ablock \quad\: \loneg MayAccess$^{Dir,Now}$(X*,o)$]$\linebreak
\ablock \ablock \ablock \quad \loor \linebreak
\ablock \ablock \ablock \quad \loneg MayAccess$^{Ind,Eve}$(X*,o')$\}$\linebreak
\ablock \loimplies\linebreak
	\ablock\loneg MayAccess$^{Ind,Eve}$(o,o')\linebreak
\hrule
\end{logic}
\end{minipage}
\textsc{epc1} has the meaning that if an object o has an eventual path to o' in some arising state \losigma', then there must exist an object X* that has an eventual path to o', and there must exist a way for o to have a path to X* in \losigma'. o either must already have a path to X* in \losigma, or that it will eventually receive the capability of X* in \losigma'. \textsc{epc1} is actually a formal representation of connectivity begets connectivity across time:

@@

\begin{logic}
\hrule\null
\textsc{\normalsize *Eventual Path Connectivity 2 (EPC2)}\\
M,\losigma\ \loturns\ MayAccess$^{Ind,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj.$\{$\linebreak
\ablock \ablock $[$\null
\textcolor{red}{\loexists X$^1$\loin{Obj}. MayAccess$^{Ind,Now}$(o, X$^1$) \loand\linebreak
\ablock \ablock \ablock \ablock \quad MayAccess$^{Dir,Now}$(X$^1$,X*)\linebreak
}
\ablock \ablock \quad \loor \linebreak
\ablock \ablock MayAccess$^{Dir,Now}$(X*,o)$ ]$\linebreak
\ablock \ablock \loand \linebreak
\textcolor{blue}{
\ablock \ablock \loexists Y*\loin Obj.$\{[$MayAccess$^{Ind,Now}$(X*,Y*)\linebreak
\ablock \ablock \ablock \ablock \quad \quad \loor \linebreak
\ablock \ablock \ablock \ablock \quad MayAccess$^{Dir,Now}$(Y*,X*)$]$\linebreak
\ablock \ablock \ablock \ablock \quad \loand \linebreak
\ablock \ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(Y*,o')$\}$
}\linebreak
\ablock \ablock $\}$
\\
\ablock \textit{where if z' exists in \losigma,} \linebreak
\ablock \loturns\ MayAccess$^{Ind,Eve}$(z',z') is true \linebreak
\\
\textit{By contraposition,}\linebreak
M,\losigma\ \loturns\ \linebreak
\ablock \loforall X*\loin Obj.$\{$\linebreak
\ablock \quad $[$\null
\textcolor{red}{\loforall X$^1$\loin{Obj}. \loneg MayAccess$^{Ind,Now}$(o,X$^1$) \loor\linebreak
\ablock \ablock \ablock \ablock \loneg MayAccess$^{Dir,Now}$(X$^1$,X*)\linebreak
}
\ablock \ablock \quad \loand \linebreak
\ablock \quad \loneg MayAccess$^{Dir,Now}$(X*,o)$ ]$\linebreak
\ablock \ablock \loor \linebreak
\textcolor{blue}{
\ablock \loforall Y*\loin Obj. $\{[$\loneg MayAccess$^{Ind,Now}$(X*,Y*)\linebreak
\ablock \ablock \ablock \ablock \quad \loand \linebreak
\ablock \ablock \ablock \quad\: \loneg MayAccess$^{Dir,Now}$(Y*,X*)$]$\linebreak
\ablock \ablock \ablock \quad \loor \linebreak
\ablock \ablock \ablock \quad \loneg MayAccess$^{Ind,Eve}$(Y*,o')$\}$
}\linebreak
\ablock \loimplies\linebreak
	\ablock\loneg MayAccess$^{Ind,Eve}(o,o')$\linebreak
\hrule
\end{logic}

@@

\begin{logic}
\hrule\null
\textsc{\normalsize *Eventual Path Connectivity 3*** (EPC3***)}\\
M,\losigma\ \loturns\ MayAccess$^{Ind,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*, x$^{1...n}$\loin Obj.$\{[$MayAccess$^{Ind,Now}$(o,o)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(o,x$^1$)\linebreak
\ablock \ablock \ablock \ablock \ablock $\vdots$\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^{n-1}$,x$^n$)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^n$,X*)$]$\linebreak
\ablock \ablock \ablock \ablock \quad\: \loor \linebreak
\ablock \ablock \ablock \ablock \quad\: MayAccess$^{Dir,Now}$(X*,o)$\}$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(X*,o')
\\
\ablock \textit{where if z' exists in \losigma,} \linebreak
\ablock \loturns\ MayAccess$^{Ind,Eve}$(z',z') is true \linebreak
\\
\hrule
\end{logic}

@@

\begin{logic}
\hrule\null
\textsc{\normalsize *Eventual Execution Connectivity (EEC)}\\
M,\losigma\ \loturns\ MayAccess$^{Dir,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj.$[($MayAccess$^{Dir,Now}$(o,X*) \loor \linebreak
\ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(X*,o)$)$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \ablock \ablock MayAccess$^{Dir,Eve}$(X*,o')$]$
\\
\ablock \textit{where if o' exists in some \losigma',}\linebreak
\ablock \loturns\ MayAccess$^{Dir,Eve}$(o',o') is true\linebreak
\\
\textit{By contraposition,}\linebreak
M,\losigma\ \loturns\ 
\loforall X*\loin Obj. $\{[$\loneg MayAccess$^{Dir,Now}$(o,X*) \loand \linebreak
\ablock \ablock \ablock \ablock \quad \loneg MayAccess$^{Dir,Now}$(X*,o)$]$\linebreak
\ablock \ablock \ablock \ablock \loor \linebreak
\ablock \ablock \ablock \ablock \loneg $[$MayAccess$^{Dir,Eve}$(X*,o')$]\}$\linebreak
\ablock \loimplies\linebreak
	\ablock\loneg MayAccess$^{Dir,Eve}(o,o')$\linebreak
\hrule
\end{logic}
The power of \textsc{eec} is similar to \textsc{epc1}\ in that it allows an arbitrary recursive expansion of the MayAccess$^{Dir,Eve}$(X*,o') till the terminating MayAccess$^{Dir,Eve}$(o',o').\\

@@

\begin{logic}
\hrule\null
\textsc{\normalsize *Necessary Path Condition 2 (NPC2)}\\
M,\losigma\ \loturns\ MayAffect$^{Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj.$[($MayAccess$^{Ind,Now}$(o,X*) \loor \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Dir,Now}$(X*,o)$)$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(X*,o')$]$
\linebreak \\
\textit{By contraposition,}\linebreak
M,\losigma\ \loturns\ 
\loforall X*\loin Obj. $[$\loneg MayAccess$^{Ind,Now}$(o,X*) \loand \linebreak
\ablock \ablock \ablock \ablock \loneg MayAccess$^{Dir,Now}$(X*,o)$]$\linebreak
\ablock \ablock \ablock \ablock \loor \linebreak
\ablock \ablock \ablock \ablock \loneg MayAccess$^{Ind,Eve}$(X*,o')$]$\linebreak
\ablock \loimplies \linebreak
	\ablock\loneg MayAffect$^{Eve}(o,o')$\linebreak
\hrule
\end{logic}
, where \textsc{npc2} is similar to \textsc{epc2}, where we can always use \textsc{gpec} to expand indirect paths into direct capabilities till we reach the terminating origin o and recursively use \textsc{epc2} to expand MayAccess$^{Ind,Eve}$(X*,o') till we reach the terminating MayAccess$^{Ind,Eve}$(o',o'). The final result through such as expansion is similar to \textsc{epc3***}. We use \textsc{epc3***} to make explicit the relationship between a configuration of direct capabilities between objects at \losigma, and the ability to modify state at some arising \losigma', which we call \textsc{ncc3***}:
\begin{logic}
\hrule\null
\textsc{\normalsize *Necessary Capability Condition 3*** (NCC3***)}\\
M,\losigma\ \loturns\ MayAffect$^{Ind,Eve}$(o,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*, x$^{1...n}$\loin Obj.$\{[$MayAccess$^{Ind,Now}$(o,o)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(o,x$^1$)\linebreak
\ablock \ablock \ablock \ablock \ablock $\vdots$\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^{n-1}$,x$^n$)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^n$,X*)$]$\linebreak
\ablock \ablock \ablock \ablock \quad\: \loor \linebreak
\ablock \ablock \ablock \ablock \quad\: MayAccess$^{Dir,Now}$(X*,o)$\}$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \ablock \quad MayAccess$^{Ind,Eve}$(X*,o')
\linebreak\\
\hrule
\end{logic}

@@

We can also show dominance by extending our necessary capability condition \textsc{ncc3***}. If we can guarantee that Y* is the only object in the system that holds the direct capability of o', and we deny Y* a direct path to o', then we know the last object in the eventual path to o' is Y* and we can simply expand the last term in \textsc{ncc3***} to state explicitly that Y* has to be the object that connects directly eventually to o':
\begin{minipage}{\linewidth}
\begin{logic}
\hrule\null
\textsc{\normalsize *Necessary Dominating Condition*** (NDC***)}\\
If Y* dominates o' then:\\
M,\losigma\ \loturns\ MayAffect$^{Ind,Eve}$(o,o') \loand\ Dom(Y*,o')\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*, x$^{1...n}$\loin Obj.$\{[$MayAccess$^{Ind,Now}$(o,o)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(o,x$^1$)\linebreak
\ablock \ablock \ablock \ablock \ablock $\vdots$\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^{n-1}$,x$^n$)\linebreak
\ablock \ablock \ablock \ablock \ablock \loand\linebreak
\ablock \ablock \ablock \ablock \ablock MayAccess$^{Dir,Now}$(x$^n$,X*)$]$\linebreak
\ablock \ablock \ablock \ablock \quad\: \loor \linebreak
\ablock \ablock \ablock \ablock \quad\: MayAccess$^{Dir,Now}$(X*,o)$\}$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \loexists Y*\loin{AttenObj}.$[$MayAccess$^{Ind,Eve}$(X*,Y*) \loand\linebreak
\ablock \ablock \ablock \ablock \ablock \quad MayAccess$^{Dir,Eve}$(Y*,o')$]$
\linebreak\\
\hrule
\end{logic}
\end{minipage}\linebreak\\
Our analysis shows the importance of attenuating objects---objects that perform their roles as \textit{defensive} objects along the eventual paths to our protected objects. If the protected object can guarantee through the system of configuration that those attenuating objects are the \textit{only} objects in the entire system that holds its capability in \textit{all} eventual states, then the protected object can dictate the conditions and degree of control on how it can be used by untrusted objects in all eventual states through those attenuating objects. This ability of the protected object to dictate control across time and conditions enables cooperation, where conditions on how the protected object will cooperate is written in those attenuating objects.\\

@@

\begin{minipage}{\linewidth}
\begin{logic}
\hrule\null
\textsc{\normalsize *Necessary Node Condition***}\\
If Y* dominates o' then:\\
M,\losigma\ \loturns\ \loforall o\loin Obj, rn\loin ReNode, n\loin Node\linebreak
ReNode\loin Obj, Node\loin Obj, RN*\losubseteq ReNode.\linebreak
\ablock MayAffect$^{Eve}$(o,n) \loand\ Dom(RN*,n)\linebreak
\ablock \loimplies\linebreak
\ablock \loexists X*\loin Obj.$[$MayAccess$^{Ind,Eve}$(o,X*)\linebreak
\ablock \ablock \ablock \ablock \quad\: \loor \linebreak
\ablock \ablock \ablock \: MayAccess$^{Dir,Now}$(X*,o)$]$\linebreak
\ablock \ablock \ablock \ablock \loand \linebreak
\ablock \ablock \loexists rn\loin{RN*}.$[$MayAccess$^{Ind,Eve}$(X*,rn) \loand\linebreak
\ablock \ablock \ablock \ablock \quad MayAccess$^{Dir,Eve}$(rn,o')$]$\linebreak\\
